The investment strategy based on behavior of artificial earthworm for use in algotrading

### 2014-05-11 Article/Article20140406Granada/LatexArt/article_main.tex
change figure position
mileage deleted
Abstract

\begin{abstract}
This paper presents an innovative concept of investment strategy derived from the general ideas of artificial intelligence. The strategy has been tested in a number of simulations on historical data and on data outside learning periods. Tests were performed mainly in the selected currency markets, including the primary currency pair EURUSD. Presented approach opens long and short positions alternately during the closing of actual candles. Closing of position is based on recommendation which is deduced from changes in characteristics of time series. The strategy has parameters that vary through time, and are adapted to the market changes. To present the strategy, a metaphor of an innovative artificial earthworm, that feeds on a time series, was used. The earthworm has its own artificial intelligence which allows it to analyse ,,consumed'' candles, change its preferences about movement direction or to stay in neutral state. The goal was to implement presented strategy for trading platform to achieve the automatic trading effect.  The strategy was tested in two development environments --- MATLAB environment and trading platform MetaTrader after conversion of M-file into MQL4 file. Implemented strategy allows to achieve interesting results.
\keywords{investment strategy, machine learning, forecasting, time series, algotrading, mql4}
\end{abstract}

@@

\begin{figure}[h!]
\centering
\includegraphics[width = 0.5\textwidth]{figures/rys8.png}
\caption{Mileage accumulation of capital for horizon of 800 steps for the currency pair EURUSD 1h. This horizon was divided into sections with constant parameter values. Test sections were preceded by learning sections with a length of 80 steps.}
\label{fig:fig8}
\end{figure}
\FloatBarrier
Tests were also made for another great important currency pair GBPUSD sampled every 1h. Results for this currency pair are worse than for EURUSD, however, they reaffirm the overall efficiency of the algorithm.\\

@@

Figure \ref{fig:fig10} presents the results for EURUSD currency pair.

From these results it can be concluded that the strategy is working with a short term duration characteristics. The best results were achieved in periods containing 10-20 candles --- unlike in any other strategy presented in \cite{Wilinski2014}, where the best results were achieved for the test periods with a length of 80-100 candles.\\
All the results presented above refer to simulations conducted in MATLAB.

\begin{figure}[h!]
\centering
\includegraphics[width = 0.5\textwidth]{figures/rys10.png}
\caption{EURUSD Results per candle.}
\label{fig:fig10}
\end{figure}
\FloatBarrier
%%PBStop

>>>>

\begin{abstract}
The paper presents an innovative concept of investment strategy derived from the general ideas of artificial intelligence. The strategy has been tested in a number of simulations on historical data as well as data outside learning periods. Tests were performed mainly in the selected currency markets, including the primary currency pair of EURUSD. Presented approach opens long and short positions alternately during candle closing events. Closing a position is based on recommendation which is deduced from changes in characteristics of time series. The strategy has parameters that vary through time and are adapted to a market changes. To present the strategy a metaphor of an innovative artificial earthworm that feeds on a time series was used. The earthworm has its own artificial intelligence which enables it to analyse ,,consumed'' candles, change its preferences about movement direction or to stay in neutral state. The goal was to implement presented strategy for trading platform to achieve the automatic trading effect.  The strategy was tested in two development environments --- MATLAB environment and trading platform MetaTrader after conversion of M-file into MQL4 file. Implemented strategy enables to achieve interesting results.
\keywords{investment strategy, machine learning, forecasting, time series, algotrading, mql4}
\end{abstract}

@@

\begin{figure}[h!]
\centering
\includegraphics[width = 0.5\textwidth]{figures/rys8.png}
\caption{Accumulation of capital for horizon of 800 steps for the currency pair EURUSD 1h. This horizon was divided into sections with constant parameter values. Test sections were preceded by learning sections with a length of 80 steps.}
\label{fig:fig8}
\end{figure}
\FloatBarrier
Tests were also made for another great important currency pair GBPUSD sampled every 1h. Results for this currency pair are worse than for EURUSD, however, they reaffirm the overall efficiency of the algorithm.\\

\begin{figure}[h!]
\centering
\includegraphics[width = 0.5\textwidth]{figures/rys10.png}
\caption{EURUSD Results per candle.}
\label{fig:fig10}
\end{figure}
\FloatBarrier

@@

Figure \ref{fig:fig10} presents the results for EURUSD currency pair. From these results it can be concluded that the strategy is working with a short term duration characteristics. The best results were achieved in periods containing 10-20 candles --- unlike in any other strategy presented in \cite{Wilinski2014}, where the best results were achieved for the test periods with a length of 80-100 candles.\\
All the results presented above refer to simulations conducted in MATLAB.

%%PBStop
